Variants of G\"{o}del's Ontological Proof \\ in a Natural Deduction Calculus

### 2016-09-10 Papers/InProgress/NaturalDeduction/GodProof-ND.tex
Reviewer 2: B: Fix box introduction in proof of iteration lemma
Fix typo

G\"odel bulit on Leibniz's work \citep{adams} and brought the ontological argument to a modern form using a modal logic with higher-order quantification over properties. In this setting, he gave precise axioms describing the notion of \emph{positive} property and defined God as a being that has all positive properties. G\"odel's work was saved in his own notes \citep{Goedel} as well as in notes by Scott \citep{scott}, in whom he confided his proof.

@@

\AXC{Brouwer's Reduction}\dashedLine
\UIC{$\pos \nec A\imp A$}\RightLabel{$\nec_I$}
\UIC{$\nec(\pos \nec A\imp A)$}
\AXC{K}\dashedLine
\UIC{$\nec(\pos \nec A\imp A)\imp (\nec\pos \nec A\imp \nec A)$}\RightLabel{$\imp_E$}
\BIC{$\nec\pos \nec A\imp \nec A$}

>>>>

G\"odel built on Leibniz's work \citep{adams} and brought the ontological argument to a modern form using a modal logic with higher-order quantification over properties. In this setting, he gave precise axioms describing the notion of \emph{positive} property and defined God as a being that has all positive properties. G\"odel's work was saved in his own notes \citep{Goedel} as well as in notes by Scott \citep{scott}, in whom he confided his proof.

@@

\AXC{$\omega:$ Brouwer's Reduction}\dashedLine
\UIC{$\omega: \pos \nec A\imp A$}\RightLabel{$\nec_I$}
\UIC{$\nec(\pos \nec A\imp A)$}
\AXC{K}\dashedLine
\UIC{$\nec(\pos \nec A\imp A)\imp (\nec\pos \nec A\imp \nec A)$}\RightLabel{$\imp_E$}
\BIC{$\nec\pos \nec A\imp \nec A$}
